\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{fancyhdr}

% Header and footer settings
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Zhanchao Yang}
\fancyhead[R]{Curriculum Vitae}
\fancyfoot[C]{\thepage}

% Section formatting
\titleformat{\section}{\bfseries\large}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\bfseries}{}{0em}{}

\begin{document}

\begin{center}
    {\LARGE \bf Zhanchao Yang} \\[2mm]
    607-644-7982 \quad | \quad \href{mailto:zhanchao@upenn.edu}{zhanchao@upenn.edu} \quad | \quad Portfolio: \href{https://bit.ly/zhanchao}{https://bit.ly/zhanchao} \\[1mm]
    510 N Broad St, Philadelphia, PA, 19130 \quad | \quad \href{https://zhanchaoyang.weebly.com/}{https://zhanchaoyang.weebly.com/}
\end{center}

\vspace{4mm}

\section*{Education}
\noindent
\textbf{University of Pennsylvania, Weitzman School of Design} (Philadelphia, PA, USA) \\\hfill \textbf{Expected: May 2026}
Master of City Planning \quad (Concentration: Sustainable Transportation and Infrastructure) \\
Master of Urban Spatial Analytics 
Overall GPA: 3.93/4.0

\vspace{2mm}
\noindent
\textbf{Binghamton University, State University of New York} \hfill Binghamton, NY, USA \\
Bachelor of Arts in Geography \quad (Minors: Environmental Studies \& Global Studies) \\
Summa Cum Laude \quad (Highest departmental honors in Geography) \hfill \textbf{May 2024} \\
Overall GPA: 3.88/4.0 \quad | \quad Dean's List (2020--2024)

\section*{Study Abroad}
\noindent
\textbf{Reykjavik University} \hfill Reykjavik, Iceland \\
Studied renewable energy and sustainability \hfill \textbf{August 2022}

\section*{Publications}
\noindent
Yang, Z., and Newberry, J. (2024). ``Accessibility or Environmental Conservation? Evaluating the relationship between Environmental Protection and Hiking Trails Accessibility via LiDAR \& Remote Sensing.'' (Manuscript in progress)

\vspace{2mm}
\noindent
\textbf{Award Archive:}
\begin{itemize}[leftmargin=*]
    \item Yang, Z. (2023). ``Accessibility or Environmental Conservation? Evaluating the Relationship Between Environmental Protection and Hiking Trails Accessibility via LiDAR \& Remote Sensing.'' GIS Day, 5. \href{https://orb.binghamton.edu/gisday/5}{https://orb.binghamton.edu/gisday/5}
    \item Yang, Z., O'Day, S., McCann, P., and Lu, I. (2022). ``Tracking the Spread of Invasive Species in the Binghamton University Natural Preserve.'' GIS Day, 4. \href{https://orb.binghamton.edu/gisday/4}{https://orb.binghamton.edu/gisday/4}
\end{itemize}

\section*{Conference Presentations}
\noindent
\textbf{Accessibility or Environmental Conservation? Evaluating the relationship between Environmental Protection and Hiking Trails Accessibility via LiDAR \& Remote Sensing} \hfill \textbf{April 2024} \\
Paper Presentation, 2024 AAG Annual Conference \\
Session: GeoAI and Deep Learning Symposium: GeoAI for Ecosystem Conservation and Sustainable Geodesign \\
American Association of Geographers, Honolulu, Hawaii.

\vspace{2mm}
\noindent
\textbf{Accessibility or Environmental Conservation? Evaluating the relationship between Environmental Protection and Hiking Trails Accessibility via LiDAR \& Remote Sensing} \hfill \textbf{October 2023} \\
Student Poster Competition, Applied Geography Conference \\
Applied Geography Conference (AGX), Pittsburgh, PA

\vspace{2mm}
\noindent
\textbf{Tracking the Spread of Invasive Species in the Binghamton University Natural Preserve} \hfill \textbf{November 2022} \\
Student Poster Competition, Binghamton University GIS Day \\
Binghamton University, Department of Geography, GIS and Remote Sensing Core Facility, Binghamton, NY

\section*{Research Experience}
\noindent
\textbf{Using Public Input, UAV, and iPhone LiDAR Technique to Evaluate the Trail Conditions and Accessibility in the Binghamton University Nature Preserve} \hfill \textbf{Sept 2023 -- April 2024} \\
\textit{Honor thesis (Highest departmental honor in Geography), Binghamton University} \\
\textit{Faculty Advisor: Dr. Jay L. Newberry, Associate Professor, Co-Undergraduate Director of Geography \\
Honor Committee: Dr. Wan Yu, Associate Professor; Dr. Thomas J. Pingel, Associate Professor}
\begin{itemize}[leftmargin=*]
    \item Conducted a public survey with over 200 participants to gather opinions on trail design.
    \item Collected and analyzed data using UAV and ground data acquisition methods.
    \item Proposed an inclusive trail improvement plan based on comparative designs.
    \item Served as a model project for student research in geospatial technology.
    \item Currently developing a web app for navigation in collaboration with University ITS.
\end{itemize}

\noindent
\textbf{Mitigating Climate Change Through Urban Planning For City of Binghamton} \hfill Feb 2023 -- May 2023 \\
\textit{Team Leader, Binghamton University (Community Engagement Research) \\
Supervised by Dr. Susan Ryan, Professor of Practice, Department of Environmental Studies}
\begin{itemize}[leftmargin=*]
    \item Led the team in addressing flood prevention and climate change challenges.
    \item Developed a planning scheme incorporating complete street and urban forestry initiatives.
    \item Conducted feasibility analysis and presented the plan to the legislative branch.
\end{itemize}

\noindent
\textbf{Tracking the Spread of Invasive Species in the Binghamton University Nature Preserve} \hfill November 2022 \\
\textit{Key Member, Faculty Advisor: Dr. Wan Yu, Associate Professor of Geography}
\begin{itemize}[leftmargin=*]
    \item Investigated invasive species (Autumn Olive and Common Reed) in the area.
    \item Utilized Survey123 for community input and ArcGIS tools for data analysis.
    \item Presented at Campus GIS Day, receiving first prize and the People's Choice Award.
\end{itemize}

\noindent
\textbf{Preservation and Conservation of Historic Sites in Paris} \hfill Jan 2021 -- Dec 2021 \\
\textit{Capstone Project, Sponsored by Global Studies Program Director Dr. William Pavlovich, Binghamton University}
\begin{itemize}[leftmargin=*]
    \item Researched historical building preservation and conservation in France using multidisciplinary approaches.
    \item Conducted literature reviews and anthropological research methods.
    \item Presented findings via an online presentation and designed promotional posters.
\end{itemize}

\section*{Local and Oral History Project}
\noindent
\textbf{Johnson City Oral History Project: Places with Hidden Stores} \hfill Feb 2024 -- July 2024 \\
\textit{Co-Principal Investigator (Co-PI) \\
Faculty Advisor: Dr. David Mixter, Assistant Professor of Anthropology}
\begin{itemize}[leftmargin=*]
    \item Collaborated with Bridgman \& Parker Dance Company and Binghamton University Civic Engagement Center.
    \item Conducted interviews with long-time residents and former factory workers.
    \item Analyzed interview audio to assess the impact of urban revitalization.
    \item Collaborated with the cinema department to produce thematic short films showcased at LUMA Music Festival.
\end{itemize}

\section*{Extracurricular Experience}
\noindent
\textbf{Graduate Research Assistant} \hfill October 2024 -- Present \\
\textit{Supervised by Dr. Erick Guerra, Professor, Department of City Planning, University of Pennsylvania}
\begin{itemize}[leftmargin=*]
    \item Analyzed Fatality Analysis Reporting System (FARS) datasets using R.
    \item Presented insights at weekly meetings with the research team.
    \item Conducted literature reviews on transportation fatalities and advanced transportation technologies.
\end{itemize}

\noindent
\textbf{Member, EML Lecturer Hiring Committee} \hfill Jan 2024 -- June 2024 \\
\textit{Supervised by Dr. Donald Lowen, Vice Provost for Undergraduate Education }
\begin{itemize}[leftmargin=*]
    \item Collaborated with Prof. Linda Sukarat and other committee members to screen candidates.
    \item Participated in 15+ online and 5 in-person interview screenings.
    \item Hosted Q\&A sessions and gathered feedback during campus visits.
\end{itemize}


\noindent
\textbf{Undergraduate Research Assistant (Near Earth Imaging Lab)} \hfill Sept 2023 -- May 2024 \\
\textit{Supervised by Dr. Thomas Pingel, Associate Professor of Geography, Director of Near-Earth Imaging Lab}
\begin{itemize}[leftmargin=*]
    \item Analyzed satellite and drone imagery using Python and R.
    \item Completed a self-paced course in cloud computing and Google Earth Engine.
    \item Presented progress during weekly lab meetings.
\end{itemize}

\noindent
\textbf{English Language Institute Mentor} \hfill July 2023 -- December 2023\\
\textit{Supervised by Prof. Linda Sukarat, Director of the English Language Institute}
\begin{itemize}[leftmargin=*]
    \item Provided academic and cultural guidance to first-year international students.
    \item Developed guidelines and note cards on academics, self-care, and stress management.
    \item Mentored nine students in both group and individual sessions.
\end{itemize}

\section*{Awards \& Honors}
\begin{itemize}[leftmargin=*]
    \item \textbf{Binghamton University President Award for Student Excellence} (Honorable Mention, 2024) \\Awarded by Binghamton University Vice President, Provost Dr. Donald Hall.
    \item \textbf{SUNY Chancellor Award for Student Excellence} (2024) \\Highest honor at SUNY for excellence in academics, leadership, and community service (nominated by Binghamton University President Harvey Stenger).
    \item \textbf{Outstanding Undergraduate Conference Presentation Award} (2024)
    \item \textbf{Harpur Edge Student Support Fund Recipient} (2024)
    \item \textbf{Undergraduate Research Awards} (2023)
    \item \textbf{Paul F. Gorman '73 Memorial Scholarship} (2023)
    \item \textbf{First Place in Student Poster Competition, Seventh and Eighth Annual GIS Day} (2022 \& 2023)
    \item \textbf{People's Choice Award in Student Poster Competition, Seventh Annual GIS Day} (2022)
\end{itemize}

\section*{Professional Memberships \& Honor Society}
\noindent
\textbf{Academic Honor Societies:} \\
\textbf{Phi Beta Kappa} (2024): National Arts \& Sciences Honor Society \\
\textbf{Gemma Theta Upsilon} (2022): International Honor Society of Geography

\vspace{2mm}
\noindent
\textbf{Professional Memberships \& Certifications:} \\
\textbf{American Association of Geographers (AAG) }(2022--present) \\
\textbf{American Planning Association (APA)} (2023--present) \\
\textbf{LEED Green Associate} (2023)

\section*{References}
\noindent
\textbf{Dr. Erick Guerra} \\
Professor, Associate Dean for Research \\
Department of City Planning, University of Pennsylvania \\
Email: \href{mailto:erickg@upenn.edu}{erickg@upenn.edu} \quad | \quad Phone: (215) 746-8234

\vspace{2mm}
\noindent
\textbf{Dr. Jay L. Newberry} \\
Associate Professor, Co-Undergraduate Director \\
Department of Geography, Binghamton University \\
Email: \href{mailto:jnewber@binghamton.edu}{jnewber@binghamton.edu} | Phone: (607) 777-3090


\vspace{2mm}
\noindent
\textbf{Dr. Wan Yu} \\
Associate Professor, Co-Undergraduate Director \\
Department of Geography, Binghamton University \\
Email: \href{mailto:wyu@binghamton.edu}{wyu@binghamton.edu} 
Phone: (607)777-6731

\end{document}
